Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-06 text/supp.tex
Add TODO to SOM fig

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.27\textwidth]{../analysis/order-level-estimates.pdf}
\caption{
TODO WILL COMBINE WITH COEFFICIENT POSTERIORS IN MAIN TEXT FIG 4
  Taxonomic-order-level posterior estimates of probability that $\nu < 10$ from
  a beta regression multilevel model accounting for the effect of time-series
  length. Estimates are at the geometric mean of time series length across all
  the data (approximately 27 time steps). Colour shading refers to the
  taxonomic classes as indicated in Fig.~\ref{fig:nu-coefs} and
  Fig.~\ref{fig:correlates} (yellow for fishes, green for insects, purple for
  birds, and red for mammals). Short vertical line segments indicate median
  posterior estimates. Long dotted vertical line throughout the figure
  indicates the median expected Pr($\nu < 10$) from the prior distribution.
}
\label{fig:order-estimates}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.27\textwidth]{../analysis/order-level-estimates.pdf}
\caption{
TODO WILL COMBINE WITH COEFFICIENT POSTERIORS IN MAIN TEXT FIG 4
TODO note that this isn't all orders!
  Taxonomic-order-level posterior estimates of probability that $\nu < 10$ from
  a beta regression multilevel model accounting for the effect of time-series
  length. Estimates are at the geometric mean of time series length across all
  the data (approximately 27 time steps). Colour shading refers to the
  taxonomic classes as indicated in Fig.~\ref{fig:nu-coefs} and
  Fig.~\ref{fig:correlates} (yellow for fishes, green for insects, purple for
  birds, and red for mammals). Short vertical line segments indicate median
  posterior estimates. Long dotted vertical line throughout the figure
  indicates the median expected Pr($\nu < 10$) from the prior distribution.
}
\label{fig:order-estimates}
\end{center}
\end{figure}
